Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-28 output/latex/manuscript.tex
acks: add funding for eMERGE and PMBB

>>>>

The Phase III of the eMERGE Network was initiated and funded by the NHGRI through the following grants:
U01 HG8657 (Group Health Cooperative/University of Washington);
U01 HG8685 (Brigham and Womens Hospital);
U01 HG8672 (Vanderbilt University Medical Center);
U01 HG8666 (Cincinnati Childrens Hospital Medical Center);
U01 HG6379 (Mayo Clinic);
U01 HG8679 (Geisinger Clinic);
U01 HG8680 (Columbia University Health Sciences);
U01 HG8684 (Childrens Hospital of Philadelphia);
U01 HG8673 (Northwestern University);
U01 HG8701 (Vanderbilt University Medical Center serving as the Coordinating Center);
U01 HG8676 (Partners Healthcare/Broad Institute);
and U01 HG8664 (Baylor College of Medicine).

The Penn Medicine BioBank (PMBB) is funded by the Perelman School of Medicine at the University of Pennsylvania, a gift from the Smilow family, and the National Center for Advancing Translational Sciences of the National Institutes of Health under CTSA Award Number UL1TR001878.
We thank D. Birtwell, H. Williams, P. Baumann and M. Risman for informatics support regarding the PMBB.
We thank the staff of the Regeneron Genetics Center for whole-exome sequencing of DNA from PMBB participants.
